Supplement 1: Different Response Distributions

### 2018-10-03 pkg/disttree/inst/draft/supplement/supplement_distributions.Rnw
revision of discussion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2305 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: ec2df34a22dfa64682a2d73fc15437c31eb03126

The comparison of the zero-censored Gaussian models from the main manuscript with the
alternative distributional specifications in this supplement reveals that a Gaussian hurdle
may lead to small improvements. However, especially for EMOS and the boosted GAMLSS model
the outcome is also considerably more variable. Therefore, overall there is no convincing
enough improvement over the zero-censored Gaussian model which is therefore the focus of
the main manuscript. Also, the distributional forest appears to be more robust against
distributional (mis-)specifications compared to the other models.

>>>>

This supplement shows that the zero-censored Gaussian models from the main
manuscript and the alternative distributional specifications in this
supplement perform at least similarly. For some combinations of models and
stations, the Gaussian hurdle leads to small improvements on average but
typically with more variability (especially for EMOS and the boosted
GAMLSS). Therefore, the main manuscript focuses on the zero-censored
Gaussian model which is well-established in the probabilistic
precipitation forecasting literature. Moreover, the distributional forest
can be shown to be rather robust against distributional
(mis-)specifications compared to the other models.

% The comparison of the zero-censored Gaussian models from the main manuscript with the
% alternative distributional specifications in this supplement reveals that a Gaussian hurdle
% may lead to small improvements. However, especially for EMOS and the boosted GAMLSS model
% the outcome is also considerably more variable. Therefore, overall there is no convincing
% enough improvement over the zero-censored Gaussian model which is therefore the focus of
% the main manuscript. Also, the distributional forest appears to be more robust against
% distributional (mis-)specifications compared to the other models.
